Single Cell Xenopus TMT Analysis

### 2020-03-02 Untitled.Rmd
added glycolysis cluster analysis

## Normalization
```{r}
protImpute <- pepTidy %>% 
  group_by(peptide,run) %>% 
  mutate(intensity = intensity / intensity[label == "126"]) %>%
  ungroup() %>%
  filter(run != "ctrl", condition != "ctrl") %>%
  #dplyr::filter(abs((intensity)) < 2*sd((pepTidy$intensity), na.rm = T)) %>%
  group_by(cell, run, label, condition, Uniprot) %>% 
  summarise(abundance = mean(intensity, na.rm = T)) %>% ungroup() %>%
  group_by(Uniprot) %>%
  mutate(abundance = abundance / mean(abundance, na.rm = T)) %>% 
  group_by(cell) %>% 
  mutate(abundance = abundance / mean(abundance, na.rm = T)) %>% 
  ungroup() %>% 
  dplyr::select(cell, Uniprot, abundance) %>% 
  spread(cell, abundance) %>%
  kNN(data = ., k = 1, impNA = TRUE) %>% as_tibble() %>% dplyr::select(Uniprot:e_131_80)

@@

ggplot(allKEGG, aes(x = medCors, y = medCV)) + geom_point(aes(color = interval)) +
  geom_label_repel(data = allKEGG, 
                  aes(label = KEGG_name), 
                  colour = 'black', 
                  size = 2,
                  force = 10)

@@

glycMat <- cor[rownames(cor) %in% glyc,colnames(cor) %in% glyc]
rownames(glycMat) <- mapIds(org.Xl.eg.db, keys = rownames(glycMat), keytype = 'UNIPROT', column = 'SYMBOL')
pheatmap(glycMat, show_colnames = T, show_rownames = T, color = mypal, breaks = seq(-1,1, by = 0.01),
         cutree_cols = 3, cutree_rows = 3)

>>>>

## Normalization
```{r}
protImpute <- pepTidy %>% 
  group_by(peptide,run) %>% 
  mutate(intensity = intensity / intensity[label == "126"]) %>%
  ungroup() %>%
  filter(run != "ctrl", condition != "ctrl") %>%
  dplyr::filter(abs((intensity)) < 2*sd((pepTidy$intensity), na.rm = T)) %>%
  group_by(cell, run, label, condition, Uniprot) %>% 
  summarise(abundance = mean(intensity, na.rm = T)) %>% ungroup() %>%
  group_by(Uniprot) %>%
  mutate(abundance = abundance / mean(abundance, na.rm = T)) %>% 
  group_by(cell) %>% 
  mutate(abundance = abundance / mean(abundance, na.rm = T)) %>% 
  ungroup() %>% 
  dplyr::select(cell, Uniprot, abundance) %>% 
  spread(cell, abundance) %>%
  kNN(data = ., k = 1, impNA = TRUE) %>% as_tibble() %>% dplyr::select(Uniprot:e_131_80)

@@

ggplot(allKEGG, aes(x = corSkew, y = medCV)) + geom_point(aes(color = interval)) +
  geom_label_repel(data = allKEGG, 
                  aes(label = KEGG_name), 
                  colour = 'black', 
                  size = 2,
                  force = 10)

@@

glycMat <- cor[rownames(cor) %in% glyc,colnames(cor) %in% glyc]
rownames(glycMat) <- mapIds(org.Xl.eg.db, keys = rownames(glycMat), keytype = 'UNIPROT', column = 'SYMBOL')

row_anno <- data.frame(cv = unlist(allKEGG$cv[1]))
rownames(row_anno) <- rownames(glycMat)

map <- pheatmap(glycMat, show_colnames = T, show_rownames = T, color = mypal, breaks = seq(-1,1, by = 0.01),
         cutree_cols = 3, cutree_rows = 3, annotation_row = row_anno)

map.clust <- cbind(t(glycMat), cluster = cutree(map$tree_row, k = 3))
map.clust[,ncol(map.clust) == 2]

glyc2 <- names(which(map.clust[,ncol(map.clust)] == 2))
totVarGroup(glyc2) / length(glyc2)
protVar %>% filter(Uniprot %in% glyc2) %>%
  summarise(meanCV = mean(cv))

glyc2 <- glycMat[which(map.clust[,ncol(map.clust)] == 2),which(map.clust[,ncol(map.clust)] == 2)]
pheatmap(glyc2,
         color = mypal, breaks = seq(-1,1, by = 0.01))

glyc2 <- tibble(GO = "Glycolysis",
       cor = glyc2[lower.tri(glyc2)])

rbind(glyc2,tibble(GO = "All",
      cor = cor[lower.tri(cor)])) %>%
  ggplot(., aes(x = cor, fill = GO, alpha = 0.75)) + geom_density() +
  geom_rug(data = glyc2)
